The Courtroom Challenge—A Conjecture on the Unavoidable Cost of LLM Verification

### 2025-07-28 main.tex
Add files via upload

Cosine and L$_2$ are special cases, but a system designer is free to
plug in any monotone metric—e.g.\ Mahalanobis distance, dot-product in a
learned embedding space, or even a hybrid score that blends semantic and
numeric keys—so long as the inequality is flipped to match the
metric's notion of proximity. Section~\ref{sec:sparse-memory-bound-tightness} analyses the cost/error trade-off
under the distance form (Lemma~\ref{lemma}), and Appendix~\ref{sec:knobs} lists this dial
among the falsifiability-critical degrees of freedom. Selecting which descriptor 
fields to embed is itself tunable; Section~\ref{sec:open-questions} (Q\ref{open-question-schema}) sketches how the Courtroom loop 
could learn or prune schema columns over time.

>>>>

Cosine and L$_2$ are special cases, but a system designer is free to
plug in any monotone metric—e.g.\ Mahalanobis distance, dot-product in a
learned embedding space, or even a hybrid score that blends semantic and
numeric keys—so long as the inequality is flipped to match the
metric's notion of proximity. Section~\ref{sec:sparse-memory-bound-tightness} analyses the cost/error trade-off
under the distance form, and Appendix~\ref{sec:knobs} lists this dial
among the falsifiability-critical degrees of freedom. Selecting which descriptor 
fields to embed is itself tunable; Section~\ref{sec:open-questions} (Q\ref{open-question-schema}) sketches how the Courtroom loop 
could learn or prune schema columns over time.
